Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-04 ms.tex
section 4 refixing

Figure~\ref{fig:stag} shows our calculation of the stagnation radius
$r_{\rm s}/r_{\rm soi}$ as a function of the wind heating parameter
$\zeta = \sqrt{v_w^{2}+\sigma_0^{2}}/\sigma_0$, with different colors
showing different values of $v_{w}$.  Cusp and core galaxies are
marked with square and triangles, respectively.  Shown for comparison
are our analytic results (eq.~[\ref{eq:rs2main}]) with solid and
dashed lines for cusp and core galaxies, respectively, calculated
assuming $\densSlope = 1$ and $\densSlope= 0.6$, respectively
(eq.~[\ref{eq:densSlope}]).

Our analytic estimates accurately reproduce the numerical results in
the high heating limit $\zeta \gg 1$ ($v_w \gg \sigma_0$; $r_{\rm s}
\lesssim r_{\rm soi}$).  However, for sufficiently low heating the
stagnation radius diverges above the analytic estimate, approaching
the stellar break radius $r_b \gg r_{\rm soi}$.  This divergence
occurs approximately when $\zeta =
\sqrt{v_w^{2}+\sigma_0^{2}}/\sigma_0 < \zeta_c \propto (r_b/r_{\rm
  soi})^{0.5(\Gamma-1)}$ (eq.~[\ref{eq:zetacrit}], Appendix
\ref{app:be}), and hence occurs at a higher value of $\zeta$ in the
case of core galaxies ($\Gamma = 0.8$) with large break radii.

As $\zeta$ approached $\zeta_c$, the results the location of the
stagnation radius will depend on the location of the break radius
$\rb$.  This explains the behavior of the two core galaxies, shown as
orange triangles vertically aligned at the same value of
$\zeta$. These correspond to models with the same black hole mass
($\Mbh = 10^8 \Msun$) and heating rate ($v_w = 600$ km s$^{-1}$) but
different values of the break radius: $r_{b} =$ 25, 50 pc (from top to
bottom). {\bf AG still needs work}

>>>>

Figure~\ref{fig:stag} shows our calculation of the stagnation radius
$r_{\rm s}/r_{\rm soi}$ as a function of the wind heating parameter
$\zeta = \sqrt{1+(v_w/\sigma_0)^{2}}$, with different colors
showing different values of $v_{w}$.  Cusp and core galaxies are
marked with square and triangles, respectively.  Shown for comparison
are our analytic results (eq.~[\ref{eq:rs2main}]) with solid and
dashed lines for cusp and core galaxies, respectively, calculated
assuming $\densSlope = 1$ and $\densSlope= 0.6$, respectively
(eq.~[\ref{eq:densSlope}]).

Our analytic estimates accurately reproduce the numerical results in
the high heating limit $\zeta \gg 1$ ($v_w \gg \sigma_0$; $r_{\rm s}
\lesssim r_{\rm soi}$).  However, for sufficiently low heating the
stagnation radius diverges above the analytic estimate, approaching
the stellar break radius $r_b \gg r_{\rm soi}$.  This divergence
occurs approximately when $\zeta < \zeta_c \propto (r_b/r_{\rm
  soi})^{0.5(\Gamma-1)}$ (eq.~[\ref{eq:zetacrit}]), which in Appendix
\ref{app:be} is shown to coincide with the critical heating below which the Bernoulli parameter of the gas decreases below unity near the stagnation radius.  This divergence of the stagnation radius to large radii hence occurs at a higher value of $\zeta$ in core galaxies ($\Gamma = 0.8$) with large break radii.  This dependence explains the behavior of the two core galaxies, shown as
orange triangles vertically aligned at the same value of
$\zeta$. These correspond to models with the same black hole mass
($\Mbh = 10^8 \Msun$) and heating rate ($v_w = 600$ km s$^{-1}$) but
different values of the break radius: $r_{b} =$ 25, 50 pc (from top to
bottom). {\bf AG still needs work.  BDM: what work? this looks sufficient to me}
